---
title: "HW2"
author: '109071503'
date: "2021/2/27"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
## Preparation
     
#### Step 1: Download customer.txt from Canvas
#### Step 2: create a variable ages
```{r}
## read file customer.txt by read.table(file, header = T, sep="")
customer<-read.table("C:/Users/dakin/Desktop/customers.txt",header = TRUE,sep="")
## check our dataframe and let age become a variable called ages
ages<-customer$age
## therefore, we can call value by index
length(ages)
```
     
## Solution to HW2
     
#### Question 1: 5th element in the original list of ages
```{r}
ages[5]
```
     
#### Question 2: fifth lowest age
```{r}
## sort ages in increasing order
sorted_ages<-sort(ages)
sorted_ages[5]
```
     
#### Question 3: Extract the five lowest ages together
```{r}
## we directly call by index
sorted_ages[1:5]
```
     
#### Question 4: Get the five highest ages by first sorting them in decreasing order first
```{r}
## sort ages in decreasing order by sort(variable, decreasing = FALSE, …)
decreasing_sorted_ages<-sort(ages, decreasing = TRUE)
decreasing_sorted_ages[1:5]
```
     
#### Question 5: the average (mean) age
```{r}
mean(ages)
```
     
#### Question 6: the standard deviation of ages
```{r}
sd(ages)
```
     
#### Question 7: Make a new variable called age_diff, with the difference between each age and the mean age
```{r}
age_diff<- ages -  mean(ages)
age_diff[1:30]
```
     
#### Question 8: the average "difference between each age and the mean age"
```{r}
## its value should be very close to zero
mean(age_diff)
```
     
#### Question 9: Visualize the raw data
```{r}
## (a) histogram
hist(ages)
## (b) density plot
plot(density(ages))
## (c) boxplot+stripchart
boxplot(ages)
stripchart(ages,add = TRUE)
```